Hydras \& Co.

### 2024-01-30 doc/epsilon0-chapter.tex
improve Alectryon output

First, we prove that, for  any \texttt{LT}-accessible term $\alpha$, $\alpha$ is 
strongly accessible too (\emph{i.e.} any well formed
term (\texttt{cons $\alpha$ $n$ $\beta$})  is accessible).

The proof is structured as an induction on $\alpha'$s accessibility. Let us consider
any  accessible term $\alpha$.

@@

Let \texttt{n:nat} and \texttt{beta:T1} such that (\texttt{cons alpha n beta}) is in normal form. 
We prove first that \texttt{beta} is accessible,  which allows us to prove by well-founded induction on \texttt{beta}, 
and natural induction on \texttt{n}, that (\texttt{cons alpha n beta}) is accessible.
The proof, quite long, can be consulted in \href{../theories/html/hydras.Epsilon0.T1.html}{Epsilon0.T1}.

>>>>

First, we prove that, for  any \texttt{LT}-accessible term $\alpha$, $\alpha$ is 
strongly accessible too.
The following proof is structured as an induction on $\alpha'$s accessibility. Let us consider
any  accessible term $\alpha$.

@@

First, we prove that, for any $n$ and $\beta$, if (\texttt{cons $\alpha$ $n$ $\beta$}) is in normal form, then
 $\beta$ is accessible.

\inputsnippets{T1/betaAcc}

The lemma \texttt{betaAcc} allows us to prove by well-founded induction on $\beta$, 
and natural induction on $n$ that (\texttt{cons $\alpha$ $n$ $\beta$}) is accessible.

\inputsnippets{T1/useBetaAcc}

The proof, quite long, can be consulted in \href{../theories/html/hydras.Epsilon0.T1.html}{Epsilon0.T1}.
